working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-09 Manuscript_draft/Manuscript_draft.Rmd
edits

Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Moreover, average effect sizes differed across species and across families, see **Figure 2**. Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just 4 species out of ten had only one donor with no overlap of the effect size confidence intervals. None of the donors had a clear stronger or weaker effect across species. When the donors were groped by family not big differences were seen, just for *S. lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap.

>>>>

Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values). Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Moreover, average effect sizes differed across species and across families, see **Figure 2**. Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just for four species out of ten, just one donor did not overlap the confidence intervals with other donors. Therefore, none of the donors had a clear stronger or weaker effect across species. When the donors were groped by family not big differences were seen, just for *S. lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap. In addition,

Now talk about the 100%, Make plot!!!!

### 2019-03-09 Manuscript_draft/Manuscript_draft.tex
edits

Results of hand cross-pollination, hand self-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seed set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, average
effect sizes differed across species and families, see \textbf{Figure
2}. Despite some variability in the effect of the different pollen
donors per species, in general terms the effect per species was
homogeneous (see \textbf{Figure 3}). When the donors were gropued by
family not big differences were seen, just for one species

>>>>

Results of hand cross-pollination, hand self-pollination, natural
selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
for table with values). Heterospecific pollen reduced seed set
significatively with the 50-50\% heterospecific pollen treatments for
65\% of the pairwise interactions p\textless{}0.05. Moreover, average
effect sizes differed across species and across families, see
\textbf{Figure 2}. Despite some variability in the effect of the
different pollen donors per species, in general terms the effect of
heterospecific pollen from the distinct nine treatments per species was
homogeneous (see \textbf{Figure 3}), just for four species out of ten,
just one donor did not overlap the confidence intervals with other
donors. Therefore, none of the donors had a clear stronger or weaker
effect across species. When the donors were groped by family not big
differences were seen, just for \emph{S. lycopersicum} the confidence
intervals of Brassicaceae and Convolvulaceae did not overlap. In
addition,

Now talk about the 100\%, Make plot!!!!
